---
title: "Screencast code"
author: "Natasha"
format: html
editor: visual
---

## Things you plan to investigate using this dataset:

-    What is the average age gap between actors in movies for specific actors as the main character?

```{=html}
<!-- -->
```
-   How do we visualize the age difference between the first seven rows of actors?

-    Does the release year of the movie change the age gap between the main characters?

-    Which of the movies made the most money on average in 2006 out of 5 chosen movies ?

-    Do movies released in June and July on average make more than movies released in December and January in 2006 ?

Stat 251 topics you plan to cover during the analysis:

1\. Data cleaning - Discussed in video starting at 00:00:55

2\. Visualizing your data efficiently - Discussed in video starting at 00:16:55

3\. Joining data - Discussed in video starting at 00:40:07

4\. Dates and Times - Discussed in video starting at 00:58:41

```{r}
library(tidyverse)
hollywood<- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-02-14/age_gaps.csv")


```

Topic 1: Data cleaning

```{r}
Hollywoodsecrets<- hollywood%>%
  select(1,2,4, 6:9, 12, 13)%>%
  filter(release_year %in% c('2004', '2006', '2008', '2010', '2012','2014','2016','2018'))

Specific<- Hollywoodsecrets%>%
  filter(actor_1_name %in% c("Adam Sandler", "Leonardo DiCaprio", "Jamie Foxx", "Tom Cruise", "Hugh Jackman", "Keira Knightley", "Cameron Diaz", "Anne Hathaway", "Mila Kunis", "Julian Moore"))

p<- ggplot(Specific, mapping = aes(x = character_1_gender, y = mean(age_difference)))

p + geom_col(fill = "blue") + labs(x = " Main Character Gender", y = "Average Age Difference", title = "Average Age Differences of Main Character by Gender")



```

Topic 2: Visualizing data

```{r}

Vis1<- hollywood%>%
  select(1,2,4, 6:9, 12, 13)%>%
  head(7)

pvis1<- ggplot(Vis1, mapping = aes(x = movie_name, y = age_difference))

pvis1 + geom_col(fill = "lightblue") + labs(x = "Movie Name", y = "Age Difference", title = "Age difference for the first 7 movies") + theme(axis.text.x = element_text(angle = 45, hjust = 1))


#vis 2 average age for chosen years

vis2<- hollywood%>%
  select(1,2,4, 6:9, 12, 13)%>%
  filter(release_year %in% c('2004', '2008','2012', '2016'))

pvis2<- ggplot(vis2, mapping = aes( x = release_year, y = mean(age_difference)))
               
pvis2 + geom_bar(stat = "identity", fill = "lightpink") + labs(x = "Year", y = "Average age", title = "Year of Movie Release and Average Age Difference")
```

Topic 3: Joining Data

```{r}

moviedata<- read_csv("movies_metadata.csv")

movie2006<- moviedata%>%
  select(9, 15, 16)%>%
  filter(year(release_date)== '2006')

Hollywood06<- hollywood%>%
  filter(release_year == '2006')

hollywoodmovie06<- inner_join(movie2006, Hollywood06, by = c("original_title" = "movie_name"))

Hollmove6<- hollywoodmovie06%>%
  distinct(original_title, revenue, .keep_all = T)%>%
  filter(original_title %in% c("The Devil Wears Prada", "Dreamgirls", "Last Holiday", "The Lake House", "Accepted"))

prevo6<- ggplot(Hollmove6, mapping = aes(x = original_title, y = revenue))

prev06 +geom_col(fill= "lightgreen")+ labs(x= "Movie Name", y = "Revenue", title = "Movie Name and revenue 2006")


```

Topic 4: Dates and Time

```{r}

library(lubridate)

Holl6DT<- hollywoodmovie06%>%
  distinct(original_title, revenue, .keep_all = T)%>%
  mutate(month = month(release_date, label = T))%>%
  filter(month %in% c("Jun", "Jul", "Dec", "Jan"))

pjjdj<- ggplot(Holl6DT, mapping = aes( x = month, y = log(revenue)))

pjjdj + geom_col(fill = "purple") + labs(x = "Month of Release", y = "Revenue", title = "Month of movie release and revenue")
```
